---
title: "team.Rmd"
author: "Jennie Huxford"
date: "9/12/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Question set (team)
Discuss how to approach the following questions with your teammate. When finished, both teammate should collaborate on a single `team.Rmd` file which include the answers to the following questions. 

### Tips on coordinating as a team: 
- You can start from Invididual 1 adding, committing, and pushing `team.Rmd`, and then Individual 2 can `git pull`
- Before you make changes to existing files or `git push`, remember to `git pull` first
- Coorindate with your teammate to avoid merge conflict!
- Make sure both teammates have modified `team.Rmd` file! Users who have modified this file can be viewed by issuing `git log team.Rmd` in the Terminal.


1 \. Run the following code line by line to figure out what it's doing. Then next to each line of code, write a comment explaining its purpose and function, including the use of any specific arguments. Comments in R are proceeded by a `#`, so that R knows not to run anything after the hashtag. 

For example: 
```{r,eval=FALSE}
plot(choco$Rating,choco$Cocoa.Pct, xlab = "Ratings", ylab = "Cocoa Percentage", pch = 2, cex=2) # creates a plot with Ratings on x-axis and Cocoa Percentage of y-axis. The symbol of points is set to be a triangle (pch=2) and the size of the points is adjusted to be larger (cex=2). 
```

If you are stuck, you can always go to R's help documentation. 


```{r, eval=FALSE}
recent_rating = choco[choco$Review.Date>2011,] #creating a new dataset from the choco data set of the review dates which are greater than 2011

unique(recent_rating$Company.Location) # NOTICE: how many countries are listed but how many levels are there? there are 54 countries listed but there are 61 levels
#length(unique(recent_rating$Company.Location))

recent_rating$Company.Location = droplevels(recent_rating$Company.Location) # the function droplevels, gets rid of the levels that are not being used or are empty. so now the number of countries listed is the same as the number of levels which is 54. So this line of code is redefining the variable company.location to have only the 54 levels of the countries listed.

head(recent_rating) #shows a preview of the data set.

cross_table = table(recent_rating$Review.Date,recent_rating$Company.Location) #creates a table with the review.date as the rows and company.location as the columns. The values within the table are the ratings for that location during that specific year.
cross_table #displays the table

which(cross_table[1,]!=0 & cross_table[2,]!=0 & cross_table[3,]!=0 & cross_table[4,]!=0 & cross_table[5,]!=0) # this statement is telling us the position or column of the countries in this table that do not have a 0 rating in the first 5 rows or years.

france_recent = subset(recent_rating,Company.Location =='France') # creating a subset from the dataset recent_rating that only includes the country France.
uk_recent = subset(recent_rating,Company.Location =='U.K.') #creating a subset from the dataset recent_rating that only includes the U.K.
germany_recent = subset(recent_rating,Company.Location=='Germany') #creating a subset from the dataset recent_rating that only includes Germany.

par(mfrow=c(2,2)) # allows the plot window to display two plots in each row and two plots in each column
color1 = ifelse(france_recent$Rating >median(france_recent$Rating), 'blue', 'green') #assigning the color blue to france when the ratings when they are greater than the median rating and then the color green to france when the ratings are less than the median rating
plot(france_recent$Cocoa.Pct ~ france_recent$Review.Date,ylim=c(50,90),col=color1,pch=18,cex=1.5,xlab="Review Date", ylab= "Cocoa Percentage", main= "France")  # creating a scatter plot of France's cocoa percentage by year.
legend('bottomright',legend=c('High Rating', 'Low Rating'),col=c('blue','green'),pch=18)
#adding a legend to the plot
color2 = ifelse(uk_recent$Rating >median(uk_recent$Rating), 'purple', 'red') #assigning the color purple to UK when the ratings when they are greater than the median rating and then the color red to the UK when the ratings are less than the median rating
plot(uk_recent$Cocoa.Pct ~ uk_recent$Review.Date,ylim=c(50,90),col=color2,pch=18,cex=1.5, xlab="Review Date", ylab= "Cocoa Percentage", main= "UK") # creating a scatter plot of the U.K's cocoa percentage by year.
legend('bottomright',legend=c('High Rating', 'Low Rating'),col=c('purple','red'),pch=18)
#adding a legend to the plot
color3 = ifelse(germany_recent$Rating > median(germany_recent$Rating), 'orange', 'yellow')  #assigning the color orange to Germany when the ratings when they are greater than the median rating and then the color yellow to Germany when the ratings are less than the median rating
plot(germany_recent$Cocoa.Pct ~ germany_recent$Review.Date,ylim=c(50,90),col=color3,pch=18,cex=1.5,xlab="Review Date", ylab= "Cocoa Percentage", main= "Germany") # creating a scatter plot of Germany's cocoa percentage by year.
legend('bottomright',legend=c('High Rating', 'Low Rating'),col=c('orange','yellow'),pch=18)
#adding a legend to the plot
```

2 \. Click Zoom on the Rstudio window (under Plots) to see the plot more clearly. How do you think the plot produced from the code above can be improved? Recommend at least one possible improvement. 
the plots could be improved by moving the legend to a spot on the plot so it is not covering up any data points.

3 \. How does the **number** of ratings (not the actual value of the rating) depend on the year? Use graphics to answer this question.
based on the histogram of the recent ratings by review date the number of ratings per year seem to increase from 2013 to 2015 and then the decrease from 2015 to 2017 and in 2017 they number is at its lowest from the 6 years.
```{r}
#hist(recent_rating$Review.Date)
```

4 \. How do ratings compare across different company locations? Focus on the three locations with the most ratings. Hint: the function `sort()` might come in handy here.
The US has the most number of ratings overall followed France and then out of the three Canada has the least number of ratings. 
Looking at the distribution of the ratings, they all have similar means, but differing ranges.
```{r}
newchoco <- choco[which(choco$Company.Location %in% c('U.S.A.', 'Canada', 'France')),]
newchoco$Company.Location <- droplevels(newchoco$Company.Location)
plot(newchoco$Rating~newchoco$Company.Location)
summary(newchoco$Rating)
```
```{r}
plot(newchoco$Company.Location~newchoco$Rating)
```



5 \. Brainstorm and write down an interesting question that can be answer from the dataset. The question should not duplicate the questions above.

Which country has the biggest range of ratings?

6 \. Bonus points (optional): Answer the question from the dataset.

Their is a tie for the largest range in ratings between Canada and the USA, France has the smallest one.
```{r}
canada<-newchoco[which(choco$Company.Location == 'Canada'),]
summary(canada$Rating)
``` 

```{r}
usa <-newchoco[which(choco$Company.Location == 'U.S.A.'),]
summary(usa$Rating)
```

```{r}
france<-newchoco[which(choco$Company.Location == 'France'),]
summary(france$Rating)
```


## Submission

In Canvas, **each team** submit an RMarkdown file and (just for insurance) the corresponding html. The file should include the following: 
  
a. the names of the team members that worked on the document.
b. a link to the github repo you were working in, the owner's Github repo name, and his/her username. We should be able to see `individual1.Rmd`, `individual2.Rmd`,   `team.Rmd` (as well as the corresponding `.html` files) in the `ds202_lab2` repository. 
c. code and answers (including graphics) to all of the questions.

**Due date: You have time until Thursday Sept. 19, 10 pm to submit the final files. **
